---
title: "Untitled"
author: "Hannah Casey"
date: '2023-02-13'
output: html_document
---

```{r}
library(dplyr)
library(MatchIt)
#install.packages("rjson")
library(rjson)
library(data.table)
set.seed(151097)
#install.packages("R.matlab")
library(R.matlab)
set.seed(151097)
```


Load in brainnetome atlas BOLD timseries (confounds removed via ICA-AROMA and aCompCor)

```{r setup, include=FALSE}

BOLD_timeseries_list <- list.files(path="/Volumes/GenScotDepression/users/hcasey/rs_fMRI_STRADL_CP_MDD/BOLD_brainnetome/",
pattern=glob2rx("*corrMatrix_atlas-power2011Dseg_timeseries.tsv"), full.names = T)

BOLD_timeseries_df_list = lapply(BOLD_timeseries_list, function(x)read.table(x, header=F)) 

## Use STRADL IDs as list names
names(BOLD_timeseries_df_list) <-  gsub("/Volumes/GenScotDepression/users/hcasey/rs_fMRI_STRADL_CP_MDD/BOLD_brainnetome//sub-|_task-resting_feature-corrMatrix_atlas-power2011Dseg_timeseries.tsv|_task-Resting_feature-corrMatrix_atlas-power2011Dseg_timeseries.tsv","", BOLD_timeseries_list)

## Remove "Buckner2011_17Networks" areas from timeseries data columns 247:263
#BOLD_timeseries_df_list <- lapply(BOLD_timeseries_df_list, "[", TRUE, -c(247:263))
```

Load in STRADL phenotypes and covariates
```{r STRADL Phenotypes, include=FALSE}
## Get STRADL phenotypes
STRADL_phenotype_QC_covariates <-  read.csv("/Volumes/GenScotDepression/users/hcasey/rs_fMRI_STRADL_CP_MDD/resources/STRADL_phenotype_QC_covariates.csv", header = T)
```

Get total number of regions available with no NaNs
```{r get non-missing regions}

## Get number of regions containing NaN in participants
NaN_regions <- NULL

STRADL_IDs <- STRADL_phenotype_QC_covariates$ID

for (participant in STRADL_IDs){
  
  NaN_regions <- c(NaN_regions, colnames(BOLD_timeseries_df_list[[participant]])[colSums(is.na(BOLD_timeseries_df_list[[participant]])) > 0])
  
}

NaN_regions <- unique(NaN_regions)
sort(as.numeric(gsub("V", "",unique(NaN_regions))))
```

Assign participants to groups based on depression, pain and comorbidity phenotypes

```{r Load in disorder phentypes}

STRADL_depression_groups <- STRADL_phenotype_QC_covariates[c("ID", "current_depression")]

STRADL_depression_groups <- subset(STRADL_depression_groups, STRADL_depression_groups$ID %in% STRADL_IDs)

```

For each STRADL participant, who passed fMRI QC and has available phenotyping data, save BOLD time series at MAT file and random group

```{r}

## Depression
depression_data_dir <- "~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/resources/BOLD/LEiDA/power/ICA/"

## Create new list to store timeseries with no NA
BOLD_timeseries_df_list_depression <- BOLD_timeseries_df_list

for (participant in STRADL_IDs){
  
  ## Identify if participant has current depression
  if (STRADL_depression_groups$current_depression[STRADL_depression_groups$ID == participant] == 1){
    group <- "_case"
  }else{
    group <- "_control"
  }
  
  ## Remove NaN values from matrix
  BOLD_timeseries_df_list_depression[[participant]] <- BOLD_timeseries_df_list_depression[[participant]][,!colnames(BOLD_timeseries_df_list_depression[[participant]]) %in% NaN_regions]
  
  ## Print "writeMat" commands to be copy and pasted - cannot be run in loop
  cat(paste0("writeMat('", depression_data_dir, participant, group, ".mat', ", paste0(participant, group)," = t(as.matrix(BOLD_timeseries_df_list_depression[['", participant, "']])))", "\n"))
}

```


```{r Save MAT files}





```

