---
title: "Untitled"
author: "Hannah Casey"
date: '2023-02-13'
output: html_document
---

```{r}
library(dplyr)
#install.packages("rjson")
library(rjson)
library(data.table)
set.seed(151097)
#install.packages("R.matlab")
library(R.matlab)
set.seed(151097)
```


Load in brainnetome atlas BOLD timseries (confounds removed via ICA-AROMA and aCompCor)

```{r setup, include=FALSE}

BOLD_timeseries_list <- list.files(path="/Volumes/GenScotDepression/users/hcasey/rs_fMRI_STRADL_CP_MDD/brainnetome/",
pattern=glob2rx("*corrMatrix2_atlas-brainnetomeCombinedDseg_timeseries.tsv"), full.names = T)

BOLD_timeseries_df_list = lapply(BOLD_timeseries_list, function(x)read.table(x, header=F)) 

## Use STRADL IDs as list names
names(BOLD_timeseries_df_list) <-  gsub("/Volumes/GenScotDepression/users/hcasey/rs_fMRI_STRADL_CP_MDD/brainnetome//sub-|_task-resting_feature-corrMatrix2_atlas-brainnetomeCombinedDseg_timeseries.tsv|_task-Resting_feature-corrMatrix2_atlas-brainnetomeCombinedDseg_timeseries.tsv","", BOLD_timeseries_list)

## Remove "Buckner2011_17Networks" areas from timeseries data columns 247:263
BOLD_timeseries_df_list <- lapply(BOLD_timeseries_df_list, "[", TRUE, -c(247:263))
```

Load in exlude.json and only keep participants who passed QC

```{r exclude particpants based on QC}
AB_exclude <- rjson::fromJSON(file = "/Volumes/GenScotDepression/users/hcasey/rs_fMRI_STRADL_CP_MDD/resources/HALFpipe_QC_exclude/AB_exclude.json")
DU_exclude <- rjson::fromJSON(file = "/Volumes/GenScotDepression/users/hcasey/rs_fMRI_STRADL_CP_MDD/resources/HALFpipe_QC_exclude/DU_exclude.json")

## combine exclude files
exclude <- c(AB_exclude, DU_exclude)

## Create dataframe summarising QC rating for STRADL participants
exclude <- Map(as.data.frame, exclude)
exclude <- rbindlist(exclude, fill=TRUE)

exclude <- exclude %>%
  group_by(sub) %>%
  mutate(exlude = ifelse((any(rating == "bad") | (n() < 6)), 1,0)) %>% ## if any rating is bad for each participant or where there are less than 6 QC ratings, exclude
  select(sub, exlude) %>%
  unique()

```

Get list of participants with acceptable BOLD timeseries available

```{r STRADL passed fMRI QC}

write.table(data.frame(ID_QCed = exclude$sub[exclude$exlude == 0]), "/Volumes/GenScotDepression/users/hcasey/rs_fMRI_STRADL_CP_MDD/resources/STRADL_ID_QCed.txt", row.names = FALSE, quote = FALSE)

```

Read in IDs of STRADl participants with available current pain / current depression phenotypes who passed fMRI QC

```{r load in QCed with phenotypes}

STRADL_IDs_fMRI_QC_pain_depression <- read.table("/Volumes/GenScotDepression/users/hcasey/rs_fMRI_STRADL_CP_MDD/resources/STRADL_ID_QCed.txt", header = T)

STRADL_IDs_fMRI_QC_pain_depression <- unique(STRADL_IDs_fMRI_QC_pain_depression$ID_QCed)
```

Get total number of regions available with no NaNs
```{r get non-missing regions}

## Get number of regions containing NaN in participants
NaN_regions <- NULL

for (participant in STRADL_IDs_fMRI_QC_pain_depression){
  
  NaN_regions <- c(NaN_regions, colnames(BOLD_timeseries_df_list[[participant]])[colSums(is.na(BOLD_timeseries_df_list[[participant]])) > 0])
  
}

NaN_regions <- unique(NaN_regions)

```

Randomly assign participants to one of two groups 

```{r Load in disorder phentypes}

STRADL_random_groups <- data.frame(IDs = STRADL_IDs_fMRI_QC_pain_depression, group = sample(c(1,2), length(STRADL_IDs_fMRI_QC_pain_depression), replace = TRUE))

```



For each STRADL participant, who passed fMRI QC and has available phenotyping data, save BOLD time series at MAT file and random group

```{r}


data_dir <- "~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/"

## Create new list to store timeseries with no NA
BOLD_timeseries_df_list_no_NA <- BOLD_timeseries_df_list


for (participant in STRADL_IDs_fMRI_QC_pain_depression){
  
  ## Identify if participant has current depression or current pain 
  if (STRADL_random_groups$group[STRADL_random_groups$ID == participant] == 1){
    random_group <- "_A"
  }else{
    random_group <- "_B"
  }
  
  ## Remove NaN values from matrix
  BOLD_timeseries_df_list_no_NA[[participant]] <- BOLD_timeseries_df_list_no_NA[[participant]][,!colnames(BOLD_timeseries_df_list_no_NA[[participant]]) %in% NaN_regions]
  
  
  ## Print "writeMat" commands to be copy and pasted - cannot be run in loop
  cat(paste0("writeMat('", data_dir, participant, random_group, ".mat', ", paste0(participant, random_group)," = t(as.matrix(BOLD_timeseries_df_list_no_NA[['", participant, "']])))", "\n"))
  
}

```

## Tagged randomly?

```{r Save MAT files}
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0010_A.mat', ST1AAB0010_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0010']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0002_A.mat', ST1AAB0002_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0002']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0007_A.mat', ST1AAB0007_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0007']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0001_B.mat', ST1AAB0001_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0001']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0005_B.mat', ST1AAB0005_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0005']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0003_B.mat', ST1AAB0003_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0003']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0008_A.mat', ST1AAB0008_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0008']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0006_B.mat', ST1AAB0006_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0006']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0011_A.mat', ST1AAB0011_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0011']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0016_A.mat', ST1AAB0016_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0016']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0013_B.mat', ST1AAB0013_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0013']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0014_A.mat', ST1AAB0014_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0014']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0019_A.mat', ST1AAB0019_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0019']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0023_A.mat', ST1AAB0023_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0023']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0026_B.mat', ST1AAB0026_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0026']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0029_B.mat', ST1AAB0029_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0029']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0028_A.mat', ST1AAB0028_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0028']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0040_B.mat', ST1AAB0040_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0040']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0032_B.mat', ST1AAB0032_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0032']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0033_A.mat', ST1AAB0033_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0033']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0036_B.mat', ST1AAB0036_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0036']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0037_A.mat', ST1AAB0037_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0037']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0039_A.mat', ST1AAB0039_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0039']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0042_B.mat', ST1AAB0042_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0042']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0046_A.mat', ST1AAB0046_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0046']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0047_B.mat', ST1AAB0047_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0047']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0048_B.mat', ST1AAB0048_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0048']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0049_B.mat', ST1AAB0049_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0049']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0050_A.mat', ST1AAB0050_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0050']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0053_B.mat', ST1AAB0053_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0053']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0054_A.mat', ST1AAB0054_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0054']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0055_B.mat', ST1AAB0055_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0055']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0057_B.mat', ST1AAB0057_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0057']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0059_B.mat', ST1AAB0059_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0059']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0058_A.mat', ST1AAB0058_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0058']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0063_B.mat', ST1AAB0063_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0063']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0064_A.mat', ST1AAB0064_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0064']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0065_A.mat', ST1AAB0065_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0065']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0070_A.mat', ST1AAB0070_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0070']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0067_A.mat', ST1AAB0067_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0067']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0073_B.mat', ST1AAB0073_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0073']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0076_A.mat', ST1AAB0076_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0076']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0078_A.mat', ST1AAB0078_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0078']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0080_B.mat', ST1AAB0080_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0080']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0081_A.mat', ST1AAB0081_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0081']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0084_A.mat', ST1AAB0084_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0084']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0086_A.mat', ST1AAB0086_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0086']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0087_B.mat', ST1AAB0087_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0087']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0088_A.mat', ST1AAB0088_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0088']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0089_A.mat', ST1AAB0089_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0089']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0094_B.mat', ST1AAB0094_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0094']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0095_A.mat', ST1AAB0095_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0095']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0096_B.mat', ST1AAB0096_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0096']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0097_A.mat', ST1AAB0097_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0097']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0099_A.mat', ST1AAB0099_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0099']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0101_A.mat', ST1AAB0101_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0101']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0102_A.mat', ST1AAB0102_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0102']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0103_A.mat', ST1AAB0103_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0103']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0105_A.mat', ST1AAB0105_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0105']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0106_A.mat', ST1AAB0106_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0106']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0109_B.mat', ST1AAB0109_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0109']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0107_B.mat', ST1AAB0107_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0107']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0108_A.mat', ST1AAB0108_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0108']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0110_B.mat', ST1AAB0110_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0110']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0112_B.mat', ST1AAB0112_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0112']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0114_A.mat', ST1AAB0114_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0114']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0115_A.mat', ST1AAB0115_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0115']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0116_A.mat', ST1AAB0116_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0116']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0118_A.mat', ST1AAB0118_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0118']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0120_B.mat', ST1AAB0120_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0120']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0121_B.mat', ST1AAB0121_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0121']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0123_B.mat', ST1AAB0123_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0123']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0126_A.mat', ST1AAB0126_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0126']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0129_B.mat', ST1AAB0129_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0129']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0130_A.mat', ST1AAB0130_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0130']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0131_B.mat', ST1AAB0131_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0131']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0132_B.mat', ST1AAB0132_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0132']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0134_B.mat', ST1AAB0134_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0134']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0135_B.mat', ST1AAB0135_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0135']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0137_A.mat', ST1AAB0137_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0137']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0138_A.mat', ST1AAB0138_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0138']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0139_A.mat', ST1AAB0139_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0139']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0142_B.mat', ST1AAB0142_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0142']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0140_A.mat', ST1AAB0140_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0140']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0143_B.mat', ST1AAB0143_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0143']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0146_B.mat', ST1AAB0146_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0146']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0144_B.mat', ST1AAB0144_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0144']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0145_B.mat', ST1AAB0145_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0145']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0150_A.mat', ST1AAB0150_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0150']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0149_B.mat', ST1AAB0149_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0149']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0151_A.mat', ST1AAB0151_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0151']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0159_B.mat', ST1AAB0159_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0159']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0160_A.mat', ST1AAB0160_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0160']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0161_A.mat', ST1AAB0161_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0161']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0164_A.mat', ST1AAB0164_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0164']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0166_B.mat', ST1AAB0166_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0166']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0176_B.mat', ST1AAB0176_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0176']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0178_B.mat', ST1AAB0178_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0178']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0181_A.mat', ST1AAB0181_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0181']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0182_B.mat', ST1AAB0182_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0182']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0183_B.mat', ST1AAB0183_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0183']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0186_A.mat', ST1AAB0186_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0186']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0185_A.mat', ST1AAB0185_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0185']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0192_A.mat', ST1AAB0192_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0192']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0195_A.mat', ST1AAB0195_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0195']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0193_B.mat', ST1AAB0193_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0193']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0197_B.mat', ST1AAB0197_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0197']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0198_A.mat', ST1AAB0198_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0198']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0199_B.mat', ST1AAB0199_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0199']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0200_B.mat', ST1AAB0200_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0200']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0201_B.mat', ST1AAB0201_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0201']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0205_B.mat', ST1AAB0205_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0205']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0212_A.mat', ST1AAB0212_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0212']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0214_A.mat', ST1AAB0214_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0214']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0215_B.mat', ST1AAB0215_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0215']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0216_B.mat', ST1AAB0216_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0216']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0217_B.mat', ST1AAB0217_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0217']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0218_B.mat', ST1AAB0218_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0218']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0225_B.mat', ST1AAB0225_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0225']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0226_B.mat', ST1AAB0226_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0226']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0228_A.mat', ST1AAB0228_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0228']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0230_B.mat', ST1AAB0230_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0230']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0234_A.mat', ST1AAB0234_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0234']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0233_B.mat', ST1AAB0233_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0233']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0237_B.mat', ST1AAB0237_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0237']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0239_A.mat', ST1AAB0239_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0239']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0240_B.mat', ST1AAB0240_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0240']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0242_A.mat', ST1AAB0242_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0242']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0246_B.mat', ST1AAB0246_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0246']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0248_A.mat', ST1AAB0248_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0248']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0250_B.mat', ST1AAB0250_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0250']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0249_A.mat', ST1AAB0249_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0249']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0251_B.mat', ST1AAB0251_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0251']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0254_A.mat', ST1AAB0254_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0254']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0255_A.mat', ST1AAB0255_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0255']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0256_A.mat', ST1AAB0256_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0256']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0257_A.mat', ST1AAB0257_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0257']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0259_B.mat', ST1AAB0259_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0259']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0268_B.mat', ST1AAB0268_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0268']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0272_A.mat', ST1AAB0272_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0272']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0273_A.mat', ST1AAB0273_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0273']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0276_B.mat', ST1AAB0276_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0276']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0280_B.mat', ST1AAB0280_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0280']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0281_A.mat', ST1AAB0281_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0281']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0282_B.mat', ST1AAB0282_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0282']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0284_B.mat', ST1AAB0284_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0284']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0285_B.mat', ST1AAB0285_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0285']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0287_B.mat', ST1AAB0287_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0287']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0353_A.mat', ST1AAB0353_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0353']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0356_A.mat', ST1AAB0356_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0356']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0357_A.mat', ST1AAB0357_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0357']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0359_B.mat', ST1AAB0359_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0359']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0444_B.mat', ST1AAB0444_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0444']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0474_A.mat', ST1AAB0474_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0474']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0466_B.mat', ST1AAB0466_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0466']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0507_B.mat', ST1AAB0507_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0507']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0520_B.mat', ST1AAB0520_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0520']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0509_A.mat', ST1AAB0509_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0509']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0528_B.mat', ST1AAB0528_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0528']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0553_A.mat', ST1AAB0553_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0553']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0289_A.mat', ST1GAB0289_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0289']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0554_B.mat', ST1AAB0554_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0554']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1AAB0563_B.mat', ST1AAB0563_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1AAB0563']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0292_B.mat', ST1GAB0292_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0292']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0293_B.mat', ST1GAB0293_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0293']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0294_B.mat', ST1GAB0294_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0294']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0295_B.mat', ST1GAB0295_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0295']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0297_B.mat', ST1GAB0297_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0297']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0301_A.mat', ST1GAB0301_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0301']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0303_A.mat', ST1GAB0303_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0303']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0302_B.mat', ST1GAB0302_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0302']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0306_B.mat', ST1GAB0306_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0306']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0307_B.mat', ST1GAB0307_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0307']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0311_B.mat', ST1GAB0311_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0311']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0312_A.mat', ST1GAB0312_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0312']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0313_A.mat', ST1GAB0313_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0313']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0314_B.mat', ST1GAB0314_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0314']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0315_A.mat', ST1GAB0315_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0315']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0318_A.mat', ST1GAB0318_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0318']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0316_A.mat', ST1GAB0316_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0316']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0317_A.mat', ST1GAB0317_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0317']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0319_A.mat', ST1GAB0319_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0319']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0320_A.mat', ST1GAB0320_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0320']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0321_A.mat', ST1GAB0321_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0321']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0322_B.mat', ST1GAB0322_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0322']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0324_A.mat', ST1GAB0324_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0324']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0325_A.mat', ST1GAB0325_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0325']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0327_B.mat', ST1GAB0327_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0327']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0328_B.mat', ST1GAB0328_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0328']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0330_A.mat', ST1GAB0330_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0330']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0331_B.mat', ST1GAB0331_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0331']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0332_B.mat', ST1GAB0332_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0332']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0334_B.mat', ST1GAB0334_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0334']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0333_B.mat', ST1GAB0333_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0333']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0335_B.mat', ST1GAB0335_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0335']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0336_A.mat', ST1GAB0336_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0336']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0337_B.mat', ST1GAB0337_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0337']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0339_B.mat', ST1GAB0339_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0339']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0341_B.mat', ST1GAB0341_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0341']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0340_B.mat', ST1GAB0340_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0340']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0342_B.mat', ST1GAB0342_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0342']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0343_A.mat', ST1GAB0343_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0343']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0344_B.mat', ST1GAB0344_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0344']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0345_B.mat', ST1GAB0345_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0345']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0346_A.mat', ST1GAB0346_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0346']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0347_A.mat', ST1GAB0347_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0347']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0349_B.mat', ST1GAB0349_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0349']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0348_B.mat', ST1GAB0348_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0348']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0350_B.mat', ST1GAB0350_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0350']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0351_B.mat', ST1GAB0351_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0351']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0352_B.mat', ST1GAB0352_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0352']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0354_B.mat', ST1GAB0354_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0354']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0360_B.mat', ST1GAB0360_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0360']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0361_B.mat', ST1GAB0361_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0361']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0362_A.mat', ST1GAB0362_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0362']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0366_A.mat', ST1GAB0366_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0366']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0367_A.mat', ST1GAB0367_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0367']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0368_A.mat', ST1GAB0368_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0368']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0370_A.mat', ST1GAB0370_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0370']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0372_A.mat', ST1GAB0372_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0372']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0373_B.mat', ST1GAB0373_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0373']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0374_B.mat', ST1GAB0374_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0374']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0375_A.mat', ST1GAB0375_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0375']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0376_B.mat', ST1GAB0376_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0376']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0377_B.mat', ST1GAB0377_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0377']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0378_B.mat', ST1GAB0378_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0378']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0379_B.mat', ST1GAB0379_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0379']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0381_A.mat', ST1GAB0381_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0381']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0382_B.mat', ST1GAB0382_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0382']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0383_B.mat', ST1GAB0383_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0383']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0387_B.mat', ST1GAB0387_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0387']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0386_B.mat', ST1GAB0386_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0386']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0388_B.mat', ST1GAB0388_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0388']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0389_A.mat', ST1GAB0389_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0389']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0391_B.mat', ST1GAB0391_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0391']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0393_A.mat', ST1GAB0393_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0393']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0392_B.mat', ST1GAB0392_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0392']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0395_B.mat', ST1GAB0395_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0395']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0397_B.mat', ST1GAB0397_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0397']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0396_B.mat', ST1GAB0396_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0396']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0398_A.mat', ST1GAB0398_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0398']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0402_B.mat', ST1GAB0402_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0402']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0400_A.mat', ST1GAB0400_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0400']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0403_B.mat', ST1GAB0403_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0403']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0405_B.mat', ST1GAB0405_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0405']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0406_B.mat', ST1GAB0406_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0406']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0407_A.mat', ST1GAB0407_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0407']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0409_B.mat', ST1GAB0409_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0409']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0411_B.mat', ST1GAB0411_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0411']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0410_A.mat', ST1GAB0410_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0410']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0412_B.mat', ST1GAB0412_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0412']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0413_A.mat', ST1GAB0413_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0413']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0414_B.mat', ST1GAB0414_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0414']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0415_B.mat', ST1GAB0415_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0415']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0416_A.mat', ST1GAB0416_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0416']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0419_B.mat', ST1GAB0419_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0419']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0418_B.mat', ST1GAB0418_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0418']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0422_B.mat', ST1GAB0422_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0422']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0423_B.mat', ST1GAB0423_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0423']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0424_A.mat', ST1GAB0424_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0424']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0425_A.mat', ST1GAB0425_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0425']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0426_B.mat', ST1GAB0426_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0426']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0427_B.mat', ST1GAB0427_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0427']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0429_B.mat', ST1GAB0429_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0429']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0430_B.mat', ST1GAB0430_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0430']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0431_A.mat', ST1GAB0431_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0431']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0432_A.mat', ST1GAB0432_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0432']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0433_B.mat', ST1GAB0433_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0433']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0435_A.mat', ST1GAB0435_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0435']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0436_A.mat', ST1GAB0436_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0436']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0437_B.mat', ST1GAB0437_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0437']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0438_B.mat', ST1GAB0438_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0438']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0439_B.mat', ST1GAB0439_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0439']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0440_B.mat', ST1GAB0440_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0440']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0442_B.mat', ST1GAB0442_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0442']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0443_B.mat', ST1GAB0443_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0443']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0445_A.mat', ST1GAB0445_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0445']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0446_A.mat', ST1GAB0446_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0446']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0447_A.mat', ST1GAB0447_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0447']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0448_B.mat', ST1GAB0448_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0448']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0449_A.mat', ST1GAB0449_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0449']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0452_B.mat', ST1GAB0452_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0452']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0450_A.mat', ST1GAB0450_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0450']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0453_A.mat', ST1GAB0453_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0453']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0454_B.mat', ST1GAB0454_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0454']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0455_B.mat', ST1GAB0455_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0455']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0456_B.mat', ST1GAB0456_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0456']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0459_B.mat', ST1GAB0459_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0459']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0458_A.mat', ST1GAB0458_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0458']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0460_B.mat', ST1GAB0460_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0460']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0461_A.mat', ST1GAB0461_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0461']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0462_B.mat', ST1GAB0462_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0462']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0463_A.mat', ST1GAB0463_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0463']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0467_B.mat', ST1GAB0467_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0467']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0469_B.mat', ST1GAB0469_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0469']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0470_B.mat', ST1GAB0470_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0470']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0472_B.mat', ST1GAB0472_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0472']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0473_B.mat', ST1GAB0473_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0473']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0476_B.mat', ST1GAB0476_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0476']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0477_A.mat', ST1GAB0477_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0477']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0479_A.mat', ST1GAB0479_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0479']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0480_A.mat', ST1GAB0480_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0480']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0482_B.mat', ST1GAB0482_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0482']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0483_A.mat', ST1GAB0483_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0483']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0484_B.mat', ST1GAB0484_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0484']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0485_A.mat', ST1GAB0485_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0485']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0486_A.mat', ST1GAB0486_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0486']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0489_B.mat', ST1GAB0489_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0489']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0490_B.mat', ST1GAB0490_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0490']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0491_A.mat', ST1GAB0491_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0491']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0492_A.mat', ST1GAB0492_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0492']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0494_A.mat', ST1GAB0494_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0494']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0493_A.mat', ST1GAB0493_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0493']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0495_B.mat', ST1GAB0495_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0495']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0496_A.mat', ST1GAB0496_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0496']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0497_A.mat', ST1GAB0497_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0497']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0498_B.mat', ST1GAB0498_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0498']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0503_B.mat', ST1GAB0503_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0503']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0499_B.mat', ST1GAB0499_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0499']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0500_B.mat', ST1GAB0500_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0500']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0504_A.mat', ST1GAB0504_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0504']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0510_B.mat', ST1GAB0510_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0510']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0512_B.mat', ST1GAB0512_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0512']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0514_A.mat', ST1GAB0514_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0514']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0515_A.mat', ST1GAB0515_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0515']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0518_B.mat', ST1GAB0518_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0518']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0516_B.mat', ST1GAB0516_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0516']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0519_A.mat', ST1GAB0519_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0519']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0522_A.mat', ST1GAB0522_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0522']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0523_A.mat', ST1GAB0523_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0523']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0529_A.mat', ST1GAB0529_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0529']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0524_A.mat', ST1GAB0524_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0524']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0527_A.mat', ST1GAB0527_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0527']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0530_B.mat', ST1GAB0530_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0530']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0533_B.mat', ST1GAB0533_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0533']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0534_B.mat', ST1GAB0534_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0534']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0536_B.mat', ST1GAB0536_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0536']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0538_B.mat', ST1GAB0538_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0538']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0539_A.mat', ST1GAB0539_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0539']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0540_B.mat', ST1GAB0540_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0540']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0541_A.mat', ST1GAB0541_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0541']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0542_A.mat', ST1GAB0542_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0542']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0543_A.mat', ST1GAB0543_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0543']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0544_B.mat', ST1GAB0544_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0544']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0549_A.mat', ST1GAB0549_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0549']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0547_A.mat', ST1GAB0547_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0547']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0550_A.mat', ST1GAB0550_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0550']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0551_A.mat', ST1GAB0551_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0551']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0552_B.mat', ST1GAB0552_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0552']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0558_A.mat', ST1GAB0558_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0558']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0560_B.mat', ST1GAB0560_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0560']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0559_B.mat', ST1GAB0559_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0559']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0561_A.mat', ST1GAB0561_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0561']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0562_A.mat', ST1GAB0562_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0562']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0564_A.mat', ST1GAB0564_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0564']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0566_B.mat', ST1GAB0566_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0566']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0570_B.mat', ST1GAB0570_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0570']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0571_A.mat', ST1GAB0571_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0571']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0573_B.mat', ST1GAB0573_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0573']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0574_B.mat', ST1GAB0574_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0574']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0575_B.mat', ST1GAB0575_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0575']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0576_A.mat', ST1GAB0576_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0576']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0577_A.mat', ST1GAB0577_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0577']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0580_A.mat', ST1GAB0580_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0580']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0579_A.mat', ST1GAB0579_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0579']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0581_A.mat', ST1GAB0581_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0581']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0583_A.mat', ST1GAB0583_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0583']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0588_A.mat', ST1GAB0588_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0588']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0584_A.mat', ST1GAB0584_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0584']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0589_B.mat', ST1GAB0589_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0589']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0590_A.mat', ST1GAB0590_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0590']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0593_A.mat', ST1GAB0593_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0593']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0591_A.mat', ST1GAB0591_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0591']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0592_B.mat', ST1GAB0592_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0592']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0598_B.mat', ST1GAB0598_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0598']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0595_B.mat', ST1GAB0595_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0595']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0599_A.mat', ST1GAB0599_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0599']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0600_B.mat', ST1GAB0600_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0600']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0601_A.mat', ST1GAB0601_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0601']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0602_B.mat', ST1GAB0602_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0602']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0605_B.mat', ST1GAB0605_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0605']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0606_B.mat', ST1GAB0606_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0606']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0607_B.mat', ST1GAB0607_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0607']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0608_B.mat', ST1GAB0608_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0608']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0612_A.mat', ST1GAB0612_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0612']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0609_A.mat', ST1GAB0609_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0609']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0610_A.mat', ST1GAB0610_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0610']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0614_A.mat', ST1GAB0614_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0614']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0615_A.mat', ST1GAB0615_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0615']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0617_A.mat', ST1GAB0617_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0617']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0618_A.mat', ST1GAB0618_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0618']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0622_A.mat', ST1GAB0622_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0622']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0621_A.mat', ST1GAB0621_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0621']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0623_B.mat', ST1GAB0623_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0623']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0624_B.mat', ST1GAB0624_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0624']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0625_B.mat', ST1GAB0625_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0625']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0627_A.mat', ST1GAB0627_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0627']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0626_B.mat', ST1GAB0626_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0626']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0629_B.mat', ST1GAB0629_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0629']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0633_A.mat', ST1GAB0633_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0633']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WAB0555_A.mat', ST1WAB0555_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WAB0555']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0634_B.mat', ST1GAB0634_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0634']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GAB0635_A.mat', ST1GAB0635_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GAB0635']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WAB0556_B.mat', ST1WAB0556_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WAB0556']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2146_B.mat', ST1GDU2146_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2146']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2061_A.mat', ST1GDU2061_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2061']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2118_B.mat', ST1GDU2118_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2118']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1ADU2471_B.mat', ST1ADU2471_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1ADU2471']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2117_A.mat', ST1GDU2117_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2117']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2112_A.mat', ST1GDU2112_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2112']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2114_B.mat', ST1GDU2114_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2114']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2113_A.mat', ST1GDU2113_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2113']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2160_A.mat', ST1GDU2160_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2160']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2184_A.mat', ST1GDU2184_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2184']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2190_A.mat', ST1GDU2190_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2190']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2200_B.mat', ST1GDU2200_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2200']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2195_B.mat', ST1GDU2195_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2195']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2196_A.mat', ST1GDU2196_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2196']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2206_B.mat', ST1GDU2206_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2206']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2224_B.mat', ST1GDU2224_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2224']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2229_B.mat', ST1GDU2229_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2229']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2230_A.mat', ST1GDU2230_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2230']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2232_B.mat', ST1GDU2232_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2232']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2233_A.mat', ST1GDU2233_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2233']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2234_B.mat', ST1GDU2234_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2234']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2237_A.mat', ST1GDU2237_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2237']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2246_B.mat', ST1GDU2246_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2246']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2247_A.mat', ST1GDU2247_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2247']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2258_B.mat', ST1GDU2258_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2258']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2262_A.mat', ST1GDU2262_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2262']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2268_B.mat', ST1GDU2268_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2268']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2263_B.mat', ST1GDU2263_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2263']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2265_B.mat', ST1GDU2265_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2265']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2266_B.mat', ST1GDU2266_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2266']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2276_B.mat', ST1GDU2276_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2276']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2267_A.mat', ST1GDU2267_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2267']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2269_B.mat', ST1GDU2269_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2269']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2270_A.mat', ST1GDU2270_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2270']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2280_B.mat', ST1GDU2280_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2280']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2281_B.mat', ST1GDU2281_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2281']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2285_B.mat', ST1GDU2285_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2285']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2286_A.mat', ST1GDU2286_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2286']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2287_A.mat', ST1GDU2287_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2287']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2288_B.mat', ST1GDU2288_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2288']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2289_A.mat', ST1GDU2289_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2289']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2291_A.mat', ST1GDU2291_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2291']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2292_A.mat', ST1GDU2292_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2292']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2293_B.mat', ST1GDU2293_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2293']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2294_A.mat', ST1GDU2294_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2294']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2296_A.mat', ST1GDU2296_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2296']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2299_A.mat', ST1GDU2299_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2299']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2295_B.mat', ST1GDU2295_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2295']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2297_B.mat', ST1GDU2297_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2297']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2301_A.mat', ST1GDU2301_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2301']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2302_B.mat', ST1GDU2302_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2302']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2305_B.mat', ST1GDU2305_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2305']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2306_A.mat', ST1GDU2306_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2306']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2317_A.mat', ST1GDU2317_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2317']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2311_A.mat', ST1GDU2311_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2311']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2309_A.mat', ST1GDU2309_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2309']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2314_A.mat', ST1GDU2314_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2314']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2310_B.mat', ST1GDU2310_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2310']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2312_B.mat', ST1GDU2312_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2312']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2313_A.mat', ST1GDU2313_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2313']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2315_B.mat', ST1GDU2315_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2315']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2319_B.mat', ST1GDU2319_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2319']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2318_B.mat', ST1GDU2318_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2318']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2320_A.mat', ST1GDU2320_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2320']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2321_A.mat', ST1GDU2321_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2321']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2328_A.mat', ST1GDU2328_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2328']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2323_A.mat', ST1GDU2323_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2323']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2325_A.mat', ST1GDU2325_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2325']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2327_A.mat', ST1GDU2327_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2327']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2330_A.mat', ST1GDU2330_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2330']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2331_A.mat', ST1GDU2331_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2331']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2344_B.mat', ST1GDU2344_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2344']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2341_B.mat', ST1GDU2341_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2341']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2338_B.mat', ST1GDU2338_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2338']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2332_A.mat', ST1GDU2332_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2332']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2337_B.mat', ST1GDU2337_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2337']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2339_B.mat', ST1GDU2339_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2339']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2345_B.mat', ST1GDU2345_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2345']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2346_B.mat', ST1GDU2346_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2346']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2347_B.mat', ST1GDU2347_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2347']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2348_B.mat', ST1GDU2348_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2348']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2349_A.mat', ST1GDU2349_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2349']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2350_B.mat', ST1GDU2350_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2350']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2353_B.mat', ST1GDU2353_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2353']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2351_B.mat', ST1GDU2351_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2351']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2352_A.mat', ST1GDU2352_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2352']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2355_A.mat', ST1GDU2355_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2355']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2354_B.mat', ST1GDU2354_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2354']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2356_A.mat', ST1GDU2356_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2356']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2359_A.mat', ST1GDU2359_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2359']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2357_B.mat', ST1GDU2357_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2357']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2358_A.mat', ST1GDU2358_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2358']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2364_A.mat', ST1GDU2364_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2364']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2360_B.mat', ST1GDU2360_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2360']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2362_A.mat', ST1GDU2362_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2362']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2363_B.mat', ST1GDU2363_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2363']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2365_A.mat', ST1GDU2365_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2365']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2367_A.mat', ST1GDU2367_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2367']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2366_B.mat', ST1GDU2366_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2366']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2373_B.mat', ST1GDU2373_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2373']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2369_B.mat', ST1GDU2369_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2369']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2372_A.mat', ST1GDU2372_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2372']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2375_B.mat', ST1GDU2375_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2375']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2374_A.mat', ST1GDU2374_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2374']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2376_B.mat', ST1GDU2376_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2376']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2377_A.mat', ST1GDU2377_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2377']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2378_B.mat', ST1GDU2378_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2378']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2379_B.mat', ST1GDU2379_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2379']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2380_A.mat', ST1GDU2380_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2380']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2382_B.mat', ST1GDU2382_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2382']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2381_B.mat', ST1GDU2381_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2381']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2384_B.mat', ST1GDU2384_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2384']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2385_A.mat', ST1GDU2385_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2385']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2388_B.mat', ST1GDU2388_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2388']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2389_B.mat', ST1GDU2389_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2389']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2390_A.mat', ST1GDU2390_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2390']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2395_B.mat', ST1GDU2395_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2395']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2393_B.mat', ST1GDU2393_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2393']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2391_B.mat', ST1GDU2391_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2391']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2399_A.mat', ST1GDU2399_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2399']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2392_A.mat', ST1GDU2392_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2392']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2396_B.mat', ST1GDU2396_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2396']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2398_B.mat', ST1GDU2398_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2398']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2397_B.mat', ST1GDU2397_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2397']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2400_B.mat', ST1GDU2400_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2400']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2401_B.mat', ST1GDU2401_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2401']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2403_A.mat', ST1GDU2403_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2403']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2404_B.mat', ST1GDU2404_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2404']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2406_B.mat', ST1GDU2406_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2406']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2405_A.mat', ST1GDU2405_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2405']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2408_B.mat', ST1GDU2408_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2408']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2411_A.mat', ST1GDU2411_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2411']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2412_A.mat', ST1GDU2412_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2412']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2414_A.mat', ST1GDU2414_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2414']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2415_B.mat', ST1GDU2415_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2415']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2416_A.mat', ST1GDU2416_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2416']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2417_A.mat', ST1GDU2417_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2417']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2419_B.mat', ST1GDU2419_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2419']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2420_A.mat', ST1GDU2420_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2420']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2421_A.mat', ST1GDU2421_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2421']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2423_A.mat', ST1GDU2423_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2423']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2422_A.mat', ST1GDU2422_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2422']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2425_A.mat', ST1GDU2425_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2425']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2424_A.mat', ST1GDU2424_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2424']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2426_A.mat', ST1GDU2426_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2426']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2427_A.mat', ST1GDU2427_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2427']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2428_B.mat', ST1GDU2428_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2428']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2432_A.mat', ST1GDU2432_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2432']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2431_B.mat', ST1GDU2431_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2431']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2429_A.mat', ST1GDU2429_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2429']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2433_A.mat', ST1GDU2433_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2433']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2435_B.mat', ST1GDU2435_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2435']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2436_B.mat', ST1GDU2436_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2436']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2449_A.mat', ST1GDU2449_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2449']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2440_B.mat', ST1GDU2440_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2440']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2448_A.mat', ST1GDU2448_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2448']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2445_A.mat', ST1GDU2445_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2445']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2453_B.mat', ST1GDU2453_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2453']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2454_A.mat', ST1GDU2454_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2454']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2450_B.mat', ST1GDU2450_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2450']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2452_B.mat', ST1GDU2452_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2452']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2456_B.mat', ST1GDU2456_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2456']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2457_A.mat', ST1GDU2457_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2457']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2459_B.mat', ST1GDU2459_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2459']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2460_B.mat', ST1GDU2460_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2460']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2461_B.mat', ST1GDU2461_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2461']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2463_A.mat', ST1GDU2463_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2463']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2462_B.mat', ST1GDU2462_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2462']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2466_A.mat', ST1GDU2466_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2466']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2465_B.mat', ST1GDU2465_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2465']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2467_A.mat', ST1GDU2467_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2467']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2470_B.mat', ST1GDU2470_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2470']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2473_B.mat', ST1GDU2473_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2473']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2474_A.mat', ST1GDU2474_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2474']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2475_A.mat', ST1GDU2475_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2475']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2479_B.mat', ST1GDU2479_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2479']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2477_A.mat', ST1GDU2477_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2477']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2478_B.mat', ST1GDU2478_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2478']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2480_B.mat', ST1GDU2480_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2480']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2482_A.mat', ST1GDU2482_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2482']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2484_A.mat', ST1GDU2484_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2484']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2485_B.mat', ST1GDU2485_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2485']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2491_A.mat', ST1GDU2491_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2491']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2486_A.mat', ST1GDU2486_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2486']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2487_B.mat', ST1GDU2487_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2487']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2489_B.mat', ST1GDU2489_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2489']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2492_B.mat', ST1GDU2492_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2492']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2494_A.mat', ST1GDU2494_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2494']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2496_B.mat', ST1GDU2496_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2496']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2497_B.mat', ST1GDU2497_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2497']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2499_A.mat', ST1GDU2499_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2499']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2500_B.mat', ST1GDU2500_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2500']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2505_B.mat', ST1GDU2505_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2505']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2502_B.mat', ST1GDU2502_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2502']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2504_B.mat', ST1GDU2504_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2504']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2507_B.mat', ST1GDU2507_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2507']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2506_B.mat', ST1GDU2506_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2506']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2508_A.mat', ST1GDU2508_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2508']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2510_A.mat', ST1GDU2510_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2510']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2511_A.mat', ST1GDU2511_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2511']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2513_B.mat', ST1GDU2513_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2513']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2514_B.mat', ST1GDU2514_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2514']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2515_A.mat', ST1GDU2515_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2515']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2516_A.mat', ST1GDU2516_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2516']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2517_B.mat', ST1GDU2517_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2517']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2518_B.mat', ST1GDU2518_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2518']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2521_A.mat', ST1GDU2521_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2521']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2522_B.mat', ST1GDU2522_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2522']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2523_B.mat', ST1GDU2523_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2523']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2524_A.mat', ST1GDU2524_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2524']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2533_A.mat', ST1GDU2533_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2533']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2529_A.mat', ST1GDU2529_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2529']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2526_B.mat', ST1GDU2526_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2526']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2528_B.mat', ST1GDU2528_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2528']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2530_B.mat', ST1GDU2530_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2530']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2532_A.mat', ST1GDU2532_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2532']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2535_A.mat', ST1GDU2535_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2535']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2540_B.mat', ST1GDU2540_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2540']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2536_A.mat', ST1GDU2536_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2536']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2543_B.mat', ST1GDU2543_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2543']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2542_B.mat', ST1GDU2542_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2542']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2544_B.mat', ST1GDU2544_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2544']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2546_A.mat', ST1GDU2546_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2546']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2547_B.mat', ST1GDU2547_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2547']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2548_A.mat', ST1GDU2548_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2548']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2550_A.mat', ST1GDU2550_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2550']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2552_A.mat', ST1GDU2552_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2552']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2553_B.mat', ST1GDU2553_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2553']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2556_B.mat', ST1GDU2556_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2556']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2555_A.mat', ST1GDU2555_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2555']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2557_B.mat', ST1GDU2557_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2557']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2559_A.mat', ST1GDU2559_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2559']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2560_A.mat', ST1GDU2560_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2560']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2561_B.mat', ST1GDU2561_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2561']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2562_B.mat', ST1GDU2562_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2562']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2563_B.mat', ST1GDU2563_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2563']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2564_B.mat', ST1GDU2564_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2564']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2565_B.mat', ST1GDU2565_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2565']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2572_B.mat', ST1GDU2572_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2572']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2568_A.mat', ST1GDU2568_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2568']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2566_A.mat', ST1GDU2566_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2566']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2569_B.mat', ST1GDU2569_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2569']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2570_A.mat', ST1GDU2570_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2570']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2571_A.mat', ST1GDU2571_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2571']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2573_A.mat', ST1GDU2573_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2573']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2574_B.mat', ST1GDU2574_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2574']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2576_B.mat', ST1GDU2576_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2576']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2575_B.mat', ST1GDU2575_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2575']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2577_A.mat', ST1GDU2577_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2577']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2578_A.mat', ST1GDU2578_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2578']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2579_A.mat', ST1GDU2579_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2579']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2580_A.mat', ST1GDU2580_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2580']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2582_A.mat', ST1GDU2582_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2582']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2583_A.mat', ST1GDU2583_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2583']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2584_B.mat', ST1GDU2584_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2584']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2585_B.mat', ST1GDU2585_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2585']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2587_A.mat', ST1GDU2587_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2587']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2586_A.mat', ST1GDU2586_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2586']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2591_B.mat', ST1GDU2591_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2591']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2588_A.mat', ST1GDU2588_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2588']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2589_B.mat', ST1GDU2589_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2589']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2590_A.mat', ST1GDU2590_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2590']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2592_B.mat', ST1GDU2592_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2592']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2593_A.mat', ST1GDU2593_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2593']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2595_A.mat', ST1GDU2595_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2595']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2596_A.mat', ST1GDU2596_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2596']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2604_B.mat', ST1GDU2604_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2604']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2601_B.mat', ST1GDU2601_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2601']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2599_B.mat', ST1GDU2599_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2599']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2600_B.mat', ST1GDU2600_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2600']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2602_A.mat', ST1GDU2602_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2602']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2606_A.mat', ST1GDU2606_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2606']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2607_B.mat', ST1GDU2607_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2607']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2613_B.mat', ST1GDU2613_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2613']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2609_A.mat', ST1GDU2609_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2609']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2610_A.mat', ST1GDU2610_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2610']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2611_A.mat', ST1GDU2611_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2611']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2614_A.mat', ST1GDU2614_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2614']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2615_A.mat', ST1GDU2615_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2615']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2616_A.mat', ST1GDU2616_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2616']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2617_B.mat', ST1GDU2617_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2617']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2619_A.mat', ST1GDU2619_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2619']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2620_A.mat', ST1GDU2620_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2620']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2621_B.mat', ST1GDU2621_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2621']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2623_B.mat', ST1GDU2623_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2623']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2625_A.mat', ST1GDU2625_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2625']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2626_A.mat', ST1GDU2626_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2626']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2627_A.mat', ST1GDU2627_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2627']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2628_B.mat', ST1GDU2628_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2628']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2629_B.mat', ST1GDU2629_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2629']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2630_B.mat', ST1GDU2630_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2630']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2632_B.mat', ST1GDU2632_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2632']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2637_B.mat', ST1GDU2637_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2637']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2631_B.mat', ST1GDU2631_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2631']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2640_B.mat', ST1GDU2640_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2640']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2636_B.mat', ST1GDU2636_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2636']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2638_A.mat', ST1GDU2638_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2638']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2639_B.mat', ST1GDU2639_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2639']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2641_B.mat', ST1GDU2641_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2641']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2642_B.mat', ST1GDU2642_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2642']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2643_A.mat', ST1GDU2643_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2643']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2651_B.mat', ST1GDU2651_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2651']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2654_A.mat', ST1GDU2654_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2654']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2657_A.mat', ST1GDU2657_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2657']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2652_A.mat', ST1GDU2652_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2652']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2661_B.mat', ST1GDU2661_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2661']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2655_A.mat', ST1GDU2655_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2655']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2656_B.mat', ST1GDU2656_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2656']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2663_B.mat', ST1GDU2663_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2663']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2664_A.mat', ST1GDU2664_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2664']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2665_A.mat', ST1GDU2665_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2665']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1GDU2666_A.mat', ST1GDU2666_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1GDU2666']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2004_A.mat', ST1WDU2004_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2004']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2002_B.mat', ST1WDU2002_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2002']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2007_A.mat', ST1WDU2007_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2007']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2006_B.mat', ST1WDU2006_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2006']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2008_B.mat', ST1WDU2008_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2008']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2009_B.mat', ST1WDU2009_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2009']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2010_A.mat', ST1WDU2010_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2010']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2012_B.mat', ST1WDU2012_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2012']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2016_A.mat', ST1WDU2016_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2016']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2011_A.mat', ST1WDU2011_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2011']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2013_A.mat', ST1WDU2013_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2013']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2014_B.mat', ST1WDU2014_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2014']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2015_B.mat', ST1WDU2015_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2015']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2017_B.mat', ST1WDU2017_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2017']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2018_B.mat', ST1WDU2018_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2018']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2019_B.mat', ST1WDU2019_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2019']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2020_A.mat', ST1WDU2020_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2020']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2023_A.mat', ST1WDU2023_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2023']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2022_A.mat', ST1WDU2022_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2022']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2024_B.mat', ST1WDU2024_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2024']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2025_B.mat', ST1WDU2025_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2025']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2027_A.mat', ST1WDU2027_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2027']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2026_B.mat', ST1WDU2026_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2026']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2034_B.mat', ST1WDU2034_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2034']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2033_B.mat', ST1WDU2033_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2033']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2032_B.mat', ST1WDU2032_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2032']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2035_B.mat', ST1WDU2035_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2035']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2036_A.mat', ST1WDU2036_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2036']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2037_A.mat', ST1WDU2037_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2037']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2038_A.mat', ST1WDU2038_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2038']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2039_A.mat', ST1WDU2039_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2039']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2042_B.mat', ST1WDU2042_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2042']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2044_B.mat', ST1WDU2044_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2044']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2043_A.mat', ST1WDU2043_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2043']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2045_A.mat', ST1WDU2045_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2045']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2048_A.mat', ST1WDU2048_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2048']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2046_B.mat', ST1WDU2046_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2046']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2047_B.mat', ST1WDU2047_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2047']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2049_B.mat', ST1WDU2049_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2049']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2052_B.mat', ST1WDU2052_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2052']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2050_A.mat', ST1WDU2050_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2050']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2055_A.mat', ST1WDU2055_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2055']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2053_A.mat', ST1WDU2053_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2053']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2054_B.mat', ST1WDU2054_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2054']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2057_B.mat', ST1WDU2057_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2057']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2056_B.mat', ST1WDU2056_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2056']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2058_B.mat', ST1WDU2058_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2058']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2060_A.mat', ST1WDU2060_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2060']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2062_B.mat', ST1WDU2062_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2062']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2065_A.mat', ST1WDU2065_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2065']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2066_B.mat', ST1WDU2066_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2066']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2067_B.mat', ST1WDU2067_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2067']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2068_B.mat', ST1WDU2068_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2068']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2071_B.mat', ST1WDU2071_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2071']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2072_B.mat', ST1WDU2072_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2072']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2074_A.mat', ST1WDU2074_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2074']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2075_A.mat', ST1WDU2075_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2075']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2076_A.mat', ST1WDU2076_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2076']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2077_B.mat', ST1WDU2077_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2077']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2078_A.mat', ST1WDU2078_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2078']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2079_A.mat', ST1WDU2079_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2079']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2080_A.mat', ST1WDU2080_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2080']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2081_A.mat', ST1WDU2081_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2081']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2084_B.mat', ST1WDU2084_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2084']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2083_A.mat', ST1WDU2083_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2083']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2085_B.mat', ST1WDU2085_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2085']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2087_B.mat', ST1WDU2087_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2087']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2086_A.mat', ST1WDU2086_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2086']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2089_A.mat', ST1WDU2089_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2089']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2090_B.mat', ST1WDU2090_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2090']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2091_B.mat', ST1WDU2091_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2091']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2094_B.mat', ST1WDU2094_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2094']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2092_A.mat', ST1WDU2092_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2092']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2093_B.mat', ST1WDU2093_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2093']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2096_A.mat', ST1WDU2096_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2096']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2095_B.mat', ST1WDU2095_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2095']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2097_B.mat', ST1WDU2097_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2097']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2098_A.mat', ST1WDU2098_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2098']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2100_A.mat', ST1WDU2100_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2100']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2099_B.mat', ST1WDU2099_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2099']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2101_A.mat', ST1WDU2101_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2101']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2102_B.mat', ST1WDU2102_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2102']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2103_B.mat', ST1WDU2103_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2103']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2104_A.mat', ST1WDU2104_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2104']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2105_A.mat', ST1WDU2105_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2105']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2106_A.mat', ST1WDU2106_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2106']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2107_A.mat', ST1WDU2107_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2107']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2108_B.mat', ST1WDU2108_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2108']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2109_A.mat', ST1WDU2109_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2109']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2110_B.mat', ST1WDU2110_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2110']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2111_B.mat', ST1WDU2111_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2111']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2121_B.mat', ST1WDU2121_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2121']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2119_A.mat', ST1WDU2119_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2119']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2120_B.mat', ST1WDU2120_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2120']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2122_B.mat', ST1WDU2122_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2122']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2123_A.mat', ST1WDU2123_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2123']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2124_A.mat', ST1WDU2124_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2124']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2125_A.mat', ST1WDU2125_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2125']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2126_A.mat', ST1WDU2126_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2126']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2128_A.mat', ST1WDU2128_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2128']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2127_A.mat', ST1WDU2127_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2127']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2132_B.mat', ST1WDU2132_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2132']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2129_A.mat', ST1WDU2129_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2129']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2130_B.mat', ST1WDU2130_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2130']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2131_B.mat', ST1WDU2131_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2131']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2133_B.mat', ST1WDU2133_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2133']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2134_A.mat', ST1WDU2134_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2134']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2136_B.mat', ST1WDU2136_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2136']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2137_A.mat', ST1WDU2137_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2137']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2138_B.mat', ST1WDU2138_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2138']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2139_A.mat', ST1WDU2139_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2139']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2142_B.mat', ST1WDU2142_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2142']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2148_B.mat', ST1WDU2148_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2148']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2151_B.mat', ST1WDU2151_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2151']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2149_B.mat', ST1WDU2149_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2149']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2150_B.mat', ST1WDU2150_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2150']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2152_B.mat', ST1WDU2152_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2152']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2153_A.mat', ST1WDU2153_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2153']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2155_B.mat', ST1WDU2155_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2155']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2156_A.mat', ST1WDU2156_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2156']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2157_B.mat', ST1WDU2157_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2157']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2158_A.mat', ST1WDU2158_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2158']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2159_B.mat', ST1WDU2159_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2159']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2161_B.mat', ST1WDU2161_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2161']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2162_A.mat', ST1WDU2162_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2162']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2164_B.mat', ST1WDU2164_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2164']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2163_B.mat', ST1WDU2163_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2163']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2170_B.mat', ST1WDU2170_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2170']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2165_B.mat', ST1WDU2165_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2165']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2166_B.mat', ST1WDU2166_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2166']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2171_B.mat', ST1WDU2171_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2171']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2173_A.mat', ST1WDU2173_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2173']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2172_A.mat', ST1WDU2172_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2172']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2177_B.mat', ST1WDU2177_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2177']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2174_A.mat', ST1WDU2174_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2174']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2175_A.mat', ST1WDU2175_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2175']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2176_A.mat', ST1WDU2176_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2176']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2178_B.mat', ST1WDU2178_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2178']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2180_B.mat', ST1WDU2180_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2180']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2179_A.mat', ST1WDU2179_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2179']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2182_A.mat', ST1WDU2182_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2182']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2183_B.mat', ST1WDU2183_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2183']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2185_B.mat', ST1WDU2185_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2185']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2186_A.mat', ST1WDU2186_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2186']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2187_B.mat', ST1WDU2187_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2187']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2191_B.mat', ST1WDU2191_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2191']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2192_B.mat', ST1WDU2192_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2192']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2188_B.mat', ST1WDU2188_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2188']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2189_B.mat', ST1WDU2189_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2189']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2193_B.mat', ST1WDU2193_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2193']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2198_A.mat', ST1WDU2198_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2198']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2197_A.mat', ST1WDU2197_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2197']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2201_A.mat', ST1WDU2201_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2201']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2202_B.mat', ST1WDU2202_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2202']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2203_A.mat', ST1WDU2203_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2203']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2209_B.mat', ST1WDU2209_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2209']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2210_A.mat', ST1WDU2210_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2210']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2211_B.mat', ST1WDU2211_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2211']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2212_A.mat', ST1WDU2212_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2212']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2213_B.mat', ST1WDU2213_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2213']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2216_B.mat', ST1WDU2216_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2216']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2221_A.mat', ST1WDU2221_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2221']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2217_A.mat', ST1WDU2217_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2217']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2218_B.mat', ST1WDU2218_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2218']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2219_B.mat', ST1WDU2219_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2219']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2220_A.mat', ST1WDU2220_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2220']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2222_A.mat', ST1WDU2222_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2222']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2226_A.mat', ST1WDU2226_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2226']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2231_B.mat', ST1WDU2231_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2231']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2245_A.mat', ST1WDU2245_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2245']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2249_B.mat', ST1WDU2249_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2249']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2250_B.mat', ST1WDU2250_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2250']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2251_B.mat', ST1WDU2251_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2251']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2252_B.mat', ST1WDU2252_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2252']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2253_B.mat', ST1WDU2253_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2253']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2260_B.mat', ST1WDU2260_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2260']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2261_B.mat', ST1WDU2261_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2261']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2264_A.mat', ST1WDU2264_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2264']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2274_B.mat', ST1WDU2274_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2274']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2277_A.mat', ST1WDU2277_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2277']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2278_A.mat', ST1WDU2278_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2278']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2441_B.mat', ST1WDU2441_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2441']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2444_A.mat', ST1WDU2444_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2444']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2649_B.mat', ST1WDU2649_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2649']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2447_B.mat', ST1WDU2447_B = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2447']])))
writeMat('~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/bin/LEiDA/LEiDA_HC/temp/ST1WDU2525_A.mat', ST1WDU2525_A = t(as.matrix(BOLD_timeseries_df_list_no_NA[['ST1WDU2525']])))
```

