---
title: "STRADL_pain_phenotype"
author: "Hannah Casey"
date: '2023-01-23'
output: html_document
---

```{r load packages, include=FALSE}
library(tidyr)
library(dplyr)
library(readr)
library(stringr)
library(data.table)
library(lubridate)
```

Load in self-reported medication at the time of STRADL MRI scan. Get total STRADL participatns who reportd not taking medication vs those who reported taking some medications.

```{r load in medication}
STRADL_self_reported_medication <- read.csv("/Volumes/GenScotDepression/users/hcasey/rs_fMRI_STRADL_CP_MDD/resources/STRADL_Meds_Freetext.csv", header = TRUE)
table(STRADL_self_reported_medication$Current_Meds == "None")
```

Split string of current medications into new row where there is a comma in "Current_Meds". 
```{r format medications}
## Seperate lists of medications into seperate rows
STRADL_self_reported_medication <- STRADL_self_reported_medication %>%               
  separate_rows(Current_Meds, sep=",") %>% ## Where there is a column in medications recorded, create a new row
  mutate(Current_Meds = toupper(Current_Meds)) %>% ## convert medication names to upper case
  mutate(Current_Meds = str_trim(Current_Meds)) ## remove white space either side of medication names
```

Load in GS prescription data to get list of analgesics prescribed to all GS

```{r load in GS prescription data and get names of all analgesics ever prescribed}
## Load in prescription data of GS
GS_prescription <- read_tsv("/Volumes/mcintosh-gs-linkage/data/patient/gs-mysql/gs_pis20_full.tsv.gz")

## Get list of analgesic medications
## 4.3.1.B0: Amitriptyline
## 10.1.1: Non-steroidal anti-inflammatory drugs
## 10.3.2: Rubefacients, topical NSAIDs, capsaicin and poultices
## 4.7: Analgesics

pain_BNF <- c("0403010B0", "100101", "100302", "0407")
GS_prescription_pain_generic <- unique(GS_prescription$approved[grepl(paste(pain_BNF, collapse = "|^"), GS_prescription$bnf)])
GS_prescription_pain_branded <- unique(GS_prescription$drug[grepl(paste(pain_BNF, collapse = "|^"), GS_prescription$bnf)])
GS_prescription_pain <- unique(c(GS_prescription_pain_generic, GS_prescription_pain_branded))

## Add two misspellings of "Amitriptyline"
GS_prescription_pain <- c(GS_prescription_pain, "AMATRIPTYLINE",  "AMITRIPILINE")

## Save list of analgesic medications
write.csv(as.data.frame(sort(GS_prescription_pain)), "~/Desktop/PhD/projects/STRADL_dynamic_rs_chronic_pain_depression/resources/analgecis_meds.csv")

```

Using drug names (both generic and branded) identify STRADL participants with self-reported analgesic drug use at time of imaging. Categorize severity of pain based on type of analgesic(s) reported.

```{r Identify self-reported analgesic used at scan}
## Indicate where analgesics were taken at time of imaging
STRADL_self_reported_medication$analgesics_self_report <- 0
STRADL_self_reported_medication$analgesics_self_report[grepl(paste(GS_prescription_pain,collapse="|"), STRADL_self_reported_medication$Current_Meds)] <- 1
```

Identify where analgesics were prescribed the month of MRI scan
```{r Indentify analgesic prescription month of MRI}
## Load prescription information for STRADL participants 
STRADL_prescription <- read_tsv("/Volumes/mcintosh-gs-linkage/data/patient/gs-mysql/st_pis20_full.tsv.gz")

## Select ID, prescription date, BNF code, approved drug name, dosage and quantity.
## Change prescription date format
STRADL_prescription <- STRADL_prescription %>%
  mutate(prescription_date =  ym(dt)) %>%
  select(id, prescription_date, bnf, approved, strength) %>%
  mutate(id = as.character(id)) %>%
  rename(ID = id)

## Load in STRADL imaging times
STRADL_MRI_date <- read_tsv("/Volumes/mcintosh-gs-linkage/data/patient/gs-mysql/st_ids.tsv.gz")

STRADL_MRI_date <- STRADL_MRI_date %>%
  mutate(MRI_date =  lubridate::floor_date(as.Date(dt, format = "%d/%m/%Y"), unit = "month")) %>% ## change data to the first of each month to match prescription data
  select(st, id, MRI_date) %>% ## limit to ID and date columns
  rename(ID = id) 

## Merge STRADL MRI date and prescription data by GS ID
STRADL_prescription_MRI_date <- left_join(STRADL_prescription, STRADL_MRI_date, by = "ID")

## Indicate imaging concurrent prescriptions 
## As prescription data is recorded by month, rather than by day, include all prescripts made in the month before and the month of MRI assessment
STRADL_prescription_MRI_date$concurrent <- 0
STRADL_prescription_MRI_date$concurrent[STRADL_prescription_MRI_date$MRI_date == STRADL_prescription_MRI_date$prescription_date] <- 1
STRADL_prescription_MRI_date$concurrent[(STRADL_prescription_MRI_date$MRI_date - STRADL_prescription_MRI_date$prescription_date) == 30] <- 1
STRADL_prescription_MRI_date$concurrent[(STRADL_prescription_MRI_date$MRI_date - STRADL_prescription_MRI_date$prescription_date) == 31] <- 1
STRADL_prescription_MRI_date$concurrent[(STRADL_prescription_MRI_date$MRI_date - STRADL_prescription_MRI_date$prescription_date) == 29] <- 1
STRADL_prescription_MRI_date$concurrent[(STRADL_prescription_MRI_date$MRI_date - STRADL_prescription_MRI_date$prescription_date) == 28] <- 1

## Indicate where concurrent analgesic were prescribed
## 4.3.1.B0: Amitriptyline
## 10.1.1: Non-steroidal anti-inflammatory drugs
## 10.3.2: Rubefacients, topical NSAIDs, capsaicin and poultices
## 4.7: Analgesics

STRADL_prescription_MRI_date$concurrent_analgesic_prescription <- 0
STRADL_prescription_MRI_date$concurrent_analgesic_prescription[STRADL_prescription_MRI_date$concurrent == 1 & grepl("^0403010B0|^100101|^100302|^0407", STRADL_prescription_MRI_date$bnf)] <- 1

## Indicate where analgesic medication, that may also be used to treat CVD was prescribed concurrent with imaging
CVD_drugs <- STRADL_prescription_MRI_date$approved[grepl("^02", STRADL_prescription_MRI_date$bnf)]
CVD_analgesics <- intersect(CVD_drugs,GS_prescription_pain )
STRADL_prescription_MRI_date$concurrent_analgesic_CVD <- 0
STRADL_prescription_MRI_date$concurrent_analgesic_CVD[STRADL_prescription_MRI_date$concurrent_analgesic_prescription & grepl(paste(CVD_analgesics, collapse = "|"),STRADL_prescription_MRI_date$approved) & grepl("^02", STRADL_prescription_MRI_date$bnf)] <- 1
table(STRADL_prescription_MRI_date$concurrent_analgesic_CVD) ## No participants found

## Get IDs with a high dose of amitriptyline prescribed - may be indication of depression treatment, not pain
IDs_concurrent_high_dose_amitriptyline <- unique(STRADL_prescription_MRI_date$st[grepl("^0403010B0", STRADL_prescription_MRI_date$bnf) &
                                                   STRADL_prescription_MRI_date$strength == "50 MG" &
                                                   STRADL_prescription_MRI_date$concurrent_analgesic_prescription == 1])
```

Get pain cases and controls

```{r identify self-reported analgesic use}
## IDs with self-reported analgesic use
IDs_self_reported_medication <- NULL
for (ID in unique(STRADL_self_reported_medication$ID)){
  
  temp <- STRADL_self_reported_medication[STRADL_self_reported_medication$ID == ID,]
  
  if(ID %in% IDs_concurrent_high_dose_amitriptyline){ ## If high dose of prescription amitriptyline
    
    temp$analgesics_self_report[grepl("AMITRIPTYLINE|AMATRIPTYLINE|AMITRIPILINE", temp$Current_Meds)] <- 0 ## Remove amitriptyline as self-reported analgesics
    
  }
  
  if(sum(temp$analgesics_self_report) == 1){ ## If there is at least one self-reported analgesic
    bin <- 1 ## Record as case
  } else{
    bin <- 0 ## Otherwise don't
  }

  if(bin){
    IDs_self_reported_medication <- c(IDs_self_reported_medication, ID)
  }
}

## Get list of those with high dose amitriptyline but no other self-reported analgesic
IDs_self_reported_amitriptyline_only <- IDs_concurrent_high_dose_amitriptyline[!IDs_concurrent_high_dose_amitriptyline %in% IDs_self_reported_medication]

## IDs with concurrent prescription analgesics
IDs_prescription <- NULL
for (ID in unique(STRADL_prescription_MRI_date$st)){
  
  temp <- STRADL_prescription_MRI_date[STRADL_prescription_MRI_date$st == ID,]
  
  if(ID %in% IDs_concurrent_high_dose_amitriptyline){ ## If high dose of prescription amitriptyline
    
    temp$concurrent_analgesic_prescription[grepl("^0403010B0", temp$bnf)] <- 0 ## Remove amitriptyline as analgesic analgesics
    
    if(sum(temp$concurrent_analgesic_prescription) > 0){ ## If at least on concurrent analgesic prescription, count as a case
      bin <- 1
    } else{
      bin <- 0 ## Otherwise don't
    }
  } else{
    
    if(sum(temp$concurrent_analgesic_prescription) > 0){ ## If one or more analgecis recorded
      bin <- 1 ## Record as case
    } else{
      bin <- 0 ## Otherwise dont
    }
  }
  
  if(bin){
    IDs_prescription <- c(IDs_prescription, ID)
  }
}

## Get list of those with high dose amitriptyline but no other prescribed analgesic
IDs_prescribed_amitriptyline_only <- IDs_concurrent_high_dose_amitriptyline[!IDs_concurrent_high_dose_amitriptyline %in% IDs_prescription]

## Get list of those with only high dose amitriptyline in both self-report and prescription medication
IDs_amitriptyline_remove <- intersect(IDs_prescribed_amitriptyline_only, IDs_self_reported_amitriptyline_only)


## Define pain cases and controls
STRADL_pain <- data.frame(ID = unique(c(STRADL_prescription_MRI_date$st, STRADL_self_reported_medication$ID)))

STRADL_pain$self_reported_analgesic <- 0
STRADL_pain$self_reported_analgesic[STRADL_pain$ID %in% IDs_self_reported_medication] <- 1

STRADL_pain$concurrent_analgesic_prescription <- 0
STRADL_pain$concurrent_analgesic_prescription[STRADL_pain$ID %in% IDs_prescription] <- 1

STRADL_pain$current_pain <- 0
STRADL_pain$current_pain[STRADL_pain$self_reported_analgesic == 1 | STRADL_pain$concurrent_analgesic_prescription == 1] <- 1
STRADL_pain$current_pain[STRADL_pain$ID %in% IDs_prescribed_amitriptyline_only] <- NA ## Remove those with only high-dose amitriptyline and not other analgesics in self-report and prescription data

table(STRADL_pain$current_pain)

```



Save pain phenotype

```{r save MDD phenotype}
write.csv(STRADL_pain, "/Volumes/GenScotDepression/users/hcasey/rs_fMRI_STRADL_CP_MDD/resources/STRADL_pain.csv", row.names = FALSE, quote = FALSE)
```

