---
title: "STRADL_comorbidity_phenotypes"
author: "Hannah Casey"
date: "2023-02-15"
output: html_document
---

The purpose of this script is to derived pain and depression comorbidity phenotypes for phenotypic and fMRI analysis in STRADL.

```{r setup, include=FALSE}
library(dplyr)
```

First, load in current MDD status (defined using QIDS) and pain level (definied using concurrent self-reported medication and linked presecription data)

```{r Load in pain and depression phenotpyes}

STRADL_current_depression <- read.csv("/Volumes/GenScotDepression/users/hcasey/rs_fMRI_STRADL_CP_MDD/resources/STRADL_MDD.csv", header = TRUE)
STRADL_pain <- read.csv("/Volumes/GenScotDepression/users/hcasey/rs_fMRI_STRADL_CP_MDD/resources/STRADL_pain.csv", header = TRUE)
```

Combine pain and depression phenotypes and get comorbidity groups

```{r get comorbidity groups}
## Merge depression and pain phenotypes together
STRADL_comorbidity <- inner_join(STRADL_current_depression, STRADL_pain[c("ID", "current_pain")], by = "ID")

## Assign each participant to a comorbidity group
STRADL_comorbidity$comorbidity <- NA
STRADL_comorbidity$comorbidity[STRADL_comorbidity$current_depression == 0 & STRADL_comorbidity$current_pain == 0] <- "Pain-Dep-" ## No depression, no pain
STRADL_comorbidity$comorbidity[STRADL_comorbidity$current_depression == 1 & STRADL_comorbidity$current_pain == 0] <- "Pain-Dep+" ## Depression, no pain
STRADL_comorbidity$comorbidity[STRADL_comorbidity$current_depression == 0 & STRADL_comorbidity$current_pain == 1] <- "Pain+Dep-" ## Depression, no pain
STRADL_comorbidity$comorbidity[STRADL_comorbidity$current_depression == 1 & STRADL_comorbidity$current_pain == 1] <- "Pain+Dep+" ## Depression, no pain

table(STRADL_comorbidity$comorbidity)
```

Save comorbidity groups in STRADL

```{r save comorbidity groups}

write.csv(STRADL_comorbidity, "/Volumes/GenScotDepression/users/hcasey/rs_fMRI_STRADL_CP_MDD/resources/STRADL_comorbidity.csv", quote = FALSE, row.names = FALSE)

```


