---
title: "Prepare STRADL phenotypes"
author: "Hannah Casey"
date: "2023-02-15"
output: html_document
---
The purpose of this script is to prepare STRADL phenotypes. This will include:
  - Combining derived phenotypes into single file
  - Removing participants without acceptable fMRI data
  - Removing related individuals

```{r setup, include=FALSE}
library(dplyr)
library(tidyverse)
library(data.table)
```


Load in pain level, current MDD and comorbidity phenotype files
```{r load in phenotypes}
STRADL_current_depression <- read.csv("/Volumes/GenScotDepression/users/hcasey/rs_fMRI_STRADL_CP_MDD/resources/STRADL_MDD.csv", header = TRUE)
STRADL_pain <- read.csv("/Volumes/GenScotDepression/users/hcasey/rs_fMRI_STRADL_CP_MDD/resources/STRADL_pain.csv", header = TRUE)
STRADL_comorbidity <- read.csv("/Volumes/GenScotDepression/users/hcasey/rs_fMRI_STRADL_CP_MDD/resources/STRADL_comorbidity.csv", header = TRUE)
```

Merge phenotypes
```{r load in phenotypes}
STRADL_phenotype <- STRADL_current_depression %>%
  full_join(STRADL_pain, by='ID') %>%
  full_join(STRADL_comorbidity[c("ID", "comorbidity")], by='ID') %>%
  select(ID, current_depression, current_pain, comorbidity, QIDS)
```

Load in STRADL bridge file
```{r load bridge file}
## Load in STRADL bridge file
STRADL_bridge <- read_tsv("/Volumes/mcintosh-gs-linkage/data/patient/gs-mysql/st_ids.tsv.gz")
STRADL_bridge$id <- as.numeric(STRADL_bridge$id)
```

Get list of participants with rs-fMRI data
```{r rs-fMRI list}
fMRI_list <- list.files("/Volumes/STRADL/Functional/Resting/Data", pattern = "*.nii")
fMRI_list <- gsub("_resting.nii", "", fMRI_list)
```

Get IDs of participants who passed fMRI QC
```{r get QC fMRI list}
## Load QC files
AB_exclude <- rjson::fromJSON(file = "/Volumes/GenScotDepression/users/hcasey/rs_fMRI_STRADL_CP_MDD/resources/HALFpipe_QC_exclude/AB_exclude.json")
DU_exclude <- rjson::fromJSON(file = "/Volumes/GenScotDepression/users/hcasey/rs_fMRI_STRADL_CP_MDD/resources/HALFpipe_QC_exclude/DU_exclude.json")

## combine exclude files
exclude <- c(AB_exclude, DU_exclude)

## Create dataframe summarising QC rating for STRADL participants
exclude <- Map(as.data.frame, exclude)
exclude <- rbindlist(exclude, fill=TRUE)

exclude <- exclude %>%
  group_by(sub) %>%
  mutate(exlude = ifelse((any(rating == "bad") | (n() < 6)), 1,0)) %>% ## if any rating is bad for each participant or where there are less than 6 QC ratings, exclude
  select(sub, exlude) %>%
  unique()

exclude$sub[exclude$exlude == 0]

## Only keep participants with acceptable fMRI data
STRADL_phenotype_QC <- STRADL_phenotype[STRADL_phenotype$ID %in% exclude$sub[exclude$exlude == 0],]
```


Load in genetic relationship matrix for GS participants and keep only STRADL participants

```{r get unrelated}
## Read in STRADL relatedness matrix
STRADL_relatedness_matrix <- read.table("/Volumes/GenScotDepression/users/hcasey/rs_fMRI_STRADL_CP_MDD/resources/STRADL_relatedness_matrix.txt", row.names = 1)
names(STRADL_relatedness_matrix) <- gsub("X", "", names(STRADL_relatedness_matrix))

## For each STRADL participant get list of participants with at least 2nd degree in STRADL
STRADL_get_relatives <- NULL

for (get_row in 1:nrow(STRADL_relatedness_matrix)){

  temp <- data_frame(IID1 = rownames(STRADL_relatedness_matrix)[get_row], IID2 = colnames(STRADL_relatedness_matrix)[STRADL_relatedness_matrix[get_row,] >= 0.25])

  STRADL_get_relatives <- rbind(STRADL_get_relatives, temp)

}

## Change GS IDs to STRDL IDs
STRADL_get_relatives$IID1 <- STRADL_bridge$st[match(STRADL_get_relatives$IID1 , STRADL_bridge$id)]
STRADL_get_relatives$IID2 <- STRADL_bridge$st[match(STRADL_get_relatives$IID2 , STRADL_bridge$id)]

## Prioritize STRADL participants with Pain+MDD+, Pain+MDD- and Pain-MDD+ (in this order)
## Get IDs of participants to prioritize
priority1 <- STRADL_phenotype$ID[STRADL_phenotype$comorbidity == "Pain+Dep+"]
priority2 <- STRADL_phenotype$ID[STRADL_phenotype$comorbidity == "Pain+Dep-"]
priority3 <- STRADL_phenotype$ID[STRADL_phenotype$comorbidity == "Pain-Dep+"]

## Remove rows where "IID1" and "IID2" are the same
STRADL_get_relatives <- STRADL_get_relatives[!STRADL_get_relatives$IID1 == STRADL_get_relatives$IID2,]

## Remove one of two rows containing the same information, e.g. IID1 = 5, IID2 = 10 and IID1 = 10, IID2 = 5
STRADL_get_relatives <- STRADL_get_relatives[!duplicated(apply(STRADL_get_relatives,1,function(x) paste(sort(x),collapse=''))),]

## Get list of participants related to high priority participants
related_priority1 <- STRADL_get_relatives$IID2[STRADL_get_relatives$IID1 %in% priority1]
related_priority1 <- c(related_priority1, STRADL_get_relatives$IID1[STRADL_get_relatives$IID2 %in% priority1])

related_priority2 <- STRADL_get_relatives$IID2[STRADL_get_relatives$IID1 %in% priority2]
related_priority2 <- c(related_priority2, STRADL_get_relatives$IID1[STRADL_get_relatives$IID2 %in% priority2])

related_priority3 <- STRADL_get_relatives$IID2[STRADL_get_relatives$IID1 %in% priority3]
related_priority3 <- c(related_priority3, STRADL_get_relatives$IID1[STRADL_get_relatives$IID2 %in% priority3])

## Move all relatives of high priority participants to left column
STRADL_get_relatives$IID1_temp <- STRADL_get_relatives$IID1
STRADL_get_relatives$IID1[STRADL_get_relatives$IID2 %in% related_priority3] <- STRADL_get_relatives$IID2[STRADL_get_relatives$IID2 %in% related_priority3]
STRADL_get_relatives$IID2[STRADL_get_relatives$IID2 %in% related_priority3] <- STRADL_get_relatives$IID1_temp[STRADL_get_relatives$IID2 %in% related_priority3]
STRADL_get_relatives$IID1_temp <- STRADL_get_relatives$IID1
STRADL_get_relatives$IID1[STRADL_get_relatives$IID2 %in% related_priority2] <- STRADL_get_relatives$IID2[STRADL_get_relatives$IID2 %in% related_priority2]
STRADL_get_relatives$IID2[STRADL_get_relatives$IID2 %in% related_priority2] <- STRADL_get_relatives$IID1_temp[STRADL_get_relatives$IID2 %in% related_priority2]
STRADL_get_relatives$IID1_temp <- STRADL_get_relatives$IID1
STRADL_get_relatives$IID1[STRADL_get_relatives$IID2 %in% related_priority1] <- STRADL_get_relatives$IID2[STRADL_get_relatives$IID2 %in% related_priority1]
STRADL_get_relatives$IID2[STRADL_get_relatives$IID2 %in% related_priority1] <- STRADL_get_relatives$IID1_temp[STRADL_get_relatives$IID2 %in% related_priority1]

## Remove those without rs-fMRI data
STRADL_phenotype_QC <- STRADL_phenotype_QC[STRADL_phenotype_QC$ID %in% fMRI_list,]

## Remove one of each related pair from phenotypes
STRADL_phenotype_QC_unrelated <- STRADL_phenotype_QC[!STRADL_phenotype_QC$ID %in% STRADL_get_relatives$IID1,]

table(STRADL_phenotype$comorbidity)
```


Get STRADL covariates
```{r STRADL covariates}
STRADL_covariates <- read.csv("/Volumes/STRADL/Collated/STRADL-Measures-Phenotypic/STRADL_Demographics.csv", header = TRUE)

STRADL_phenotype_QC_covariates <- STRADL_phenotype_QC_unrelated %>%
  left_join(STRADL_covariates) %>%
  mutate(Site = ifelse(grepl("AB", ID), "AB", "DU"))  %>%
  mutate(Age_squared = Age*Age)

## Save phenotypes and covariates 
write.csv(STRADL_phenotype_QC_covariates, "/Volumes/GenScotDepression/users/hcasey/rs_fMRI_STRADL_CP_MDD/resources/STRADL_phenotype_QC_covariates.csv", row.names = FALSE, quote = FALSE)
```



